Evaluating Storage Systems for Scientific Data in the Cloud

### 2014-07-02 paper.tex
sm comments
small change

-- Persistence
Can the data be persisted in the system beyond a single run? Beyond the lifecycle of a VM?

@@

@@

@@

>>>>

-- Persistence
Can the data be persisted in the system beyond a single run? Beyond the lifecycle of a VM? "Persistent aggregation of Storage Infrastructure", This is an idea proposed by Mike a while ago. We push data to the /scratch or dev/shm of a large system. We aggregate it via one of the storage solutions: Chirp, Mosa, HDFS. We let it stay there for a longer term and allow users to do multiple non-continuous analyses on that data over time.

@@

-- The cloud storage pyramid. Elaborate and expand. Could be quite informative.

@@

A scheme and related development/implementation to push subsequent updates to software to the cloud image as part of its maintenance and upgradation.

@@

-- "Cloud provisioning from spot market", My recent work of cloud resource provisioning. A user can attach/detach cloud resources to a running application from spot market. This will also address the cost concern of cloud systems, as commented by a reviewer.
-- Provisioned IOPS? Find more about this.
-- network weather on the global backbone
-- Data management in the cloud is a hot research topic.
